Capturing Subdiffusive Solute Dynamics and Predicting Selectivity in Nanoscale Pores with Time Series Modeling

### 2020-04-17 Ben_Manuscripts/stochastic_transport/Final_Draft_JPCB.tex
Tweaks.
Cover letter for JPCB

\DeclareUnicodeCharacter{03C9}{$\omega$}
%\usepackage[en]{babel}

@@

  \graphicspath{{./figures/}}

@@

  %MRS11: in this paragraph, the ``we can'' is vague, and doesn't
  %abscribe agency.  Is ``We'' our group? Is it the field as whole?
  %If it's something someone has done in the past, there should be
  %citations. If it's something that can be done in the future, the
  %phrasing should be a long the lines of ``it is possible to'', ``it
  %can be done'', etc.

@@

  %MRS11: should be clear if first model is previous publications, or what is presented here.
  %If what is presented here, should talk about how it will be presented, not that it was developed. 
  %MRS11: research activities happened in the past, presentation of research is described in the present.
  %or potentially future if describing what will be presented in the rest of the paper. 
  %BJC: replacement to above.
  %BJC1: Made clear that this is talking about the first model of this work.
  %BJC1: went through rest of intro to make sure tense is consistent
  The first model that we develop in this work, allows us to characterize the 
  hopping and trapping behavior displayed by solutes in our MD simulations. This 
  type of non-Brownian dynamical behavior results in subdiffusive transport which
  is well-described by anomalous diffusion (AD) theory.~\cite{metzler_random_2000,bouchaud_anomalous_1990,klages_anomalous_2008}

  % BJC: focused following paragraph (RWF doesn't need to be talked about) and 
  % stole thesis from paragraph below it
  We treat our system in terms of two well-known classes of anomalous
  subdiffusion: fractional Brownian motion (FBM) subordinate to a 
  continuous time random walk (CTRW), or subordinated FBM (sFBM) for short. 
  FBM is common in crowded, viscoelastic environments where each jump comes 
  from a Gaussian distribution but is anti-correlated to its previous steps.
  ~\cite{mandelbrot_fractional_1968,jeon_fractional_2010,banks_anomalous_2005}
  A pure CTRW is characterized by a distribution of hop lengths and dwell times, 
  where trajectories consist of sequential independent random draws from each
  distribution.~\cite{montroll_random_1965} If the draws are not independent,
  then the hop sequence generation process can be described as subordinate to
  the CTRW. In our case, we observe anti-correlated draws from the hop distribution
  suggesting an FBM process is subordinate to the CTRW.

@@

  %MRS11: Introduction should not really give the answer so far.
  %Introduction should describe the questions that will bbe asked, but
  %not answer them.  That's not what is expected in an intro, it may confuse people (answers should be in the abstract).
  %MRS11: this next paragraph could use tweaks/cutting the most, but review the previous paragraphs as well.
  %MRS11: you can think about putting some of these results into conclusion, though - it reads well now, but might be benefitted from reemphasizing results if it's currently missing any of this.
  %BJC2: slight tweaks and removed conclusions from following paragraph. Also went back through previous
  % paragraphs to look for conclusions.

@@

  We ran all MD simulations and energy minimizations using GROMACS
  2018~\cite{bekker_gromacs:_1993,berendsen_gromacs:_1995,van_der_spoel_gromacs:_2005,hess_gromacs_2008}.
  We performed all post-simulation trajectory analysis using Python scripts
  which are available online at
  \texttt{https://github.com/shirtsgroup/LLC\_Membranes}.  The appropriate
  scripts to use for subsequent calculations are summarized in
  Table~\ref{S-table:python_scripts} of the Supplemental Material.

@@

  Analogous to power law dwell times, the heavy tails of L\'evy stable hop
  length distributions result in rare but arbitrarily long hops. These long and
  unrealistic hops result in over-estimated simulated MSDs (see
  Figure~\ref{fig:ad_realizations_1mode} for example). We observe that the
  distribution of hops observed in our MD simulations are well approximated by
  L\'evy stable distributions close to the mean, but they significantly
  under-sample the tails. We chose to truncate the L\'evy stable distributions
  based on where the theoretical probability distribution function (PDF) starts
  to deviate from the empirically measured PDF (see
  Section~\ref{S-section:truncation} of the Supplemental
  Material).~\cite{mantegna_stochastic_1994}

@@

  We used the Python package \texttt{fbm}~\cite{flynn_fbm_2019} to generate exact simulations of FBM
  and our own Python implementation (see Table~\ref{S-table:python_scripts} of
  the Supporting Information) of the algorithm by Stoev and Taqqu to
  simulate FLM.~\cite{stoev_simulation_2004} Note that, to our knowledge, there
  are no known exact simulation algorithms for generating FLM trajectories.
  However, the algorithm we used sufficiently approximates draws from the
  marginal L\'evy stable distribution and reasonably approximates the
  correlation structure on MD simulation timescales. We added an empirical
  correction to enhance the accuracy of the correlation structure (see
  Section~\ref{S-section:flm_correlation} of the Supporting Information for
  validation of the approach).

@@

  Several of the choices of AD models and parameters we have described yield
  qualitatively similar trajectories to those seen in our MD simulations.  In
  Figure~\ref{fig:ad_eyetest}, we plot representative sample trajectories for
  each combination of the dwell time and hop distribution, labeled according to
  Table~\ref{table:anomalous_models}. The sFBMcut and sFLMcut in particular
  resemble the trajectories in Figure~\ref{fig:solute_trajectories}.  When we
  do not truncate the dwell time distribution, the trajectories tend to
  incorporate very long dwell times as shown by the sFBM and sFLM models.
  Predictions made with these models consistently under-predict the MD MSDs
  (see Figure~\ref{S-fig:anomalous_msds_bothmode} of the Supplemental
  Material). Therefore, we will not include the pure sFBM or sFLM models in the
  remainder of our analysis.

@@

  It is computationally infeasible to simulate trajectories long enough that
  they traverse the length of a macroscopic pore. To date, the thinnest
  H\textsubscript{II} LLC membrane synthesized with the monomer in this work
  was 7$\mu$m thick.~\cite{feng_thin_2016}
  Using 24 cores to simulate trajectory realizations in
  parallel, it takes on the order of 1 day to simulate 10000 sFBMcut
  realizations of solutes traversing a 50 nm pore. The RAM requirements and
  performance scales greater than linearly and thus would take an infeasible
  amount of memory and time to simulate transport through a pore over 100 times
  longer. One could improve performance significantly by simulating less
  trajectories. In Figure~\ref{S-fig:flux_curve_sensitivity} of the Supplemental
  Material, we determined that one can simulate as few as 100 sFBMcut
  realizations in order to parameterize Equation~\ref{eqn:flux_decay}. For
  better precision, we recommend simulating at least 1000 realizations.
  However, even with an order of magnitude decrease in number of trajectories,
  it is still infeasible to simulate experimental-length pores.

@@

  % No TOC image in PRE
  %\section*{TOC Graphic}

  %\begin{figure}[!htb]
  %\centering
  %\includegraphics[width=3.25in]{toc.pdf}
  %\end{figure}

>>>>

\usepackage[utf8]{inputenc}
\DeclareUnicodeCharacter{03C9}{$\omega$}
%\usepackage[en]{babel}

@@

  \graphicspath{{./figures/arxiv_figures/}}

@@

  %MRS11: in this paragraph, the ``we can'' is vague, and doesn't
  %ascribe agency.  Is ``We'' our group? Is it the field as whole?
  %If it's something someone has done in the past, there should be
  %citations. If it's something that can be done in the future, the
  %phrasing should be a long the lines of ``it is possible to'', ``it
  %can be done'', etc.

@@

  %MRS11: should be clear if first model is previous publications, or what is presented here.
  %If what is presented here, should talk about how it will be presented, not that it was developed. 
  %MRS11: research activities happened in the past, presentation of research is described in the present.
  %or potentially future if describing what will be presented in the rest of the paper. 
  %BJC: replacement to above.
  %BJC1: Made clear that this is talking about the first model of this work.
  %BJC1: went through rest of intro to make sure tense is consistent
  The first model that we develop in this work allows us to characterize the 
  hopping and trapping behavior displayed by solutes in our MD simulations. This 
  type of non-Brownian dynamical behavior results in subdiffusive transport which
  is well-described by anomalous diffusion (AD) theory.~\cite{metzler_random_2000,bouchaud_anomalous_1990,klages_anomalous_2008}
  %MRS12: removing paragraph break
  % BJC: focused following paragraph (RWF doesn't need to be talked about) and 
  % stole thesis from paragraph below it
  We treat our system in terms of two well-known classes of anomalous
  subdiffusion: fractional Brownian motion (FBM) subordinate to a 
  continuous time random walk (CTRW), or subordinated FBM (sFBM) for short. 
  FBM is common in crowded, viscoelastic environments where each jump comes 
  from a Gaussian distribution but is anti-correlated to its previous steps.
  ~\cite{mandelbrot_fractional_1968,jeon_fractional_2010,banks_anomalous_2005}
  A pure CTRW is characterized by a distribution of hop lengths and dwell times, 
  where trajectories consist of sequential independent random draws from each
  distribution.~\cite{montroll_random_1965} If the draws are not independent,
  then the hop sequence generation process can be described as subordinate to
  the CTRW. In our case, we observe anti-correlated draws from the hop distribution
  suggesting an FBM process is subordinate to the CTRW.

@@

  %MRS11: Introduction should not really give the answer so far.
  %Introduction should describe the questions that will be asked, but
  %not answer them.  That's not what is expected in an intro, it may confuse people (answers should be in the abstract).
  %MRS11: this next paragraph could use tweaks/cutting the most, but review the previous paragraphs as well.
  %MRS11: you can think about putting some of these results into conclusion, though - it reads well now, but might be benefited from reemphasizing results if it's currently missing any of this.
  %BJC2: slight tweaks and removed conclusions from following paragraph. Also went back through previous
  % paragraphs to look for conclusions.

@@

  We ran all MD simulations and energy minimizations using GROMACS
  2018~\cite{bekker_gromacs:_1993,berendsen_gromacs:_1995,van_der_spoel_gromacs:_2005,hess_gromacs_2008}.
  We performed all post-simulation trajectory analysis using Python scripts
  which are available online at
  \texttt{https://github.com/shirtsgroup/LLC\_Membranes}.  The appropriate
  scripts to use for subsequent calculations are summarized in
  Table~\ref{S-table:python_scripts} of the Supporting Information.

@@

  Analogous to power law dwell times, the heavy tails of L\'evy stable hop
  length distributions result in rare but arbitrarily long hops. These long and
  unrealistic hops result in over-estimated simulated MSDs (see
  Figure~\ref{fig:ad_realizations_1mode} for example). We observe that the
  distribution of hops observed in our MD simulations are well approximated by
  L\'evy stable distributions close to the mean, but they significantly
  under-sample the tails. We chose to truncate the L\'evy stable distributions
  based on where the theoretical probability distribution function (PDF) starts
  to deviate from the empirically measured PDF (see
  Section~\ref{S-section:truncation} of the Supporting Information).~\cite{mantegna_stochastic_1994}

@@

  We used the Python package \texttt{fbm}~\cite{flynn_exact_2019} to generate exact simulations of FBM
  and our own Python implementation (see Table~\ref{S-table:python_scripts} of
  the Supporting Information) of the algorithm by Stoev and Taqqu to
  simulate FLM.~\cite{stoev_simulation_2004} Note that, to our knowledge, there
  are no known exact simulation algorithms for generating FLM trajectories.
  However, the algorithm we used sufficiently approximates draws from the
  marginal L\'evy stable distribution and reasonably approximates the
  correlation structure on MD simulation timescales. We added an empirical
  correction to enhance the accuracy of the correlation structure (see
  Section~\ref{S-section:flm_correlation} of the Supporting Information for
  validation of the approach).

@@

  Several of the choices of AD models and parameters we have described yield
  qualitatively similar trajectories to those seen in our MD simulations.  In
  Figure~\ref{fig:ad_eyetest}, we plot representative sample trajectories for
  each combination of the dwell time and hop distribution, labeled according to
  Table~\ref{table:anomalous_models}. The sFBMcut and sFLMcut in particular
  resemble the trajectories in Figure~\ref{fig:solute_trajectories}.  When we
  do not truncate the dwell time distribution, the trajectories tend to
  incorporate very long dwell times as shown by the sFBM and sFLM models.
  Predictions made with these models consistently under-predict the MD MSDs
  (see Figure~\ref{S-fig:anomalous_msds_bothmode} of the Supporting Information).
  Therefore, we will not include the pure sFBM or sFLM models in the
  remainder of our analysis.

@@

  It is computationally infeasible to simulate trajectories long enough that
  they traverse the length of a macroscopic pore. To date, the thinnest
  H\textsubscript{II} LLC membrane synthesized with the monomer in this work
  was 7$\mu$m thick.~\cite{feng_thin_2016}
  Using 24 cores to simulate trajectory realizations in
  parallel, it takes on the order of 1 day to simulate 10000 sFBMcut
  realizations of solutes traversing a 50 nm pore. The RAM requirements and
  performance scales greater than linearly and thus would take an infeasible
  amount of memory and time to simulate transport through a pore over 100 times
  longer. One could improve performance significantly by simulating less
  trajectories. In Figure~\ref{S-fig:flux_curve_sensitivity} of the Supporting
  Information, we determined that one can simulate as few as 100 sFBMcut
  realizations in order to parameterize Equation~\ref{eqn:flux_decay}. For
  better precision, we recommend simulating at least 1000 realizations.
  However, even with an order of magnitude decrease in number of trajectories,
  it is still infeasible to simulate experimental-length pores.

@@

  % No TOC image in PRE
  \section*{TOC Graphic}

  \begin{figure}[!htb]
  \centering
  \includegraphics[width=3.25in]{toc.pdf}
  \end{figure}
